### 2020-03-16 Article.tex
Cuarentena1

@@

Let $G^1$ and $G^2$ be hypergraphs, and let
$V_1:=V(G^1), V_2:=V(G^2)$.
Let $\overline{v} \in V_1^*, 
\overline{u} \in V_2^*$ be tuples of the same length.
We say that $\overline{v}$ and $\overline{u}$ have
$k$-\textbf{similar} $r$-neighborhoods, written as
$(G^1,\overline{v})\simeq_{k,r}(G^2 \overline{u})$, if Duplicator wins
$d\ehr_k\big(N(\overline{v};r),
\overline{v};\, N(\overline{u};r),\overline{u}\big)$.\par
Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
we say that $X$ and $Y$ have $k$-\textbf{similar}
$r$-neighborhoods, written as
$X\simeq_{k,r} Y$, if we can order their elements to form
lists $\overline{v}$, resp. $\overline{u}$ such that 
$(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$.
\par
Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
$Y\subseteq V_2$ can
be partitioned into sets $X=X_1\cup \dots \cup X_a$
and $Y=Y_1\cup \dots \cup Y_b$ 
such that $N(X_i;r)$'s, and the
$N(Y_i;r)$'s, are connected and disjoint. 
We say that $X$ and
$Y$ have $k$-\textbf{agreeable} $r$-neighborhoods,
written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
among the $X_i$'s or the $Y_i$'s
it is satisfied that ``the number of $X_i$'s  
such that $(G^\delta, Z) \simeq_{k,r} (G^1,X_i)$ 
and the number of $Y_i$'s such that
$(G^\delta,Z)\simeq_{k,r} (G^2,Y_i)$
are both equal or are both greater 
or equal than $k$" .

@@

\begin{theorem}\label{ThmDuplicator}
	Set $r=(3^k-1)/2$.
	Let $G^1,G^2$ be hypergraphs and let $V_1:=V(G^1)$, $V_2:=
	V(G^2)$.
	Suppose there exist
	sets $X\subseteq V_1$, $Y\subseteq V_2$ with the 
	following properties:
	\begin{enumerate}
		\item[(1)] $(G^1,X)\cong_{k,r} (G^2,Y)$.
		\item[(2)] Let $r^\prime\leq r$. Let $v\in V_1$ be
		a vertex such that $d(X,v)> 2r^\prime + 1$. Let 
		$\overline{u}\in (V_2)^{k-1}$ be a tuple of vertices. 
		Then there exists $u\in V_2$ such that 
		$d(u,\overline{u})>2r^\prime+1$,
		$d(Y,u)>2r^\prime +1$ and
		$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$.	
		\item[(3)] Let $r^\prime\leq r$. Let $u\in V_2$ be
		a vertex such that $d(Y,u)> 2r^\prime + 1$. Let 
		$\overline{v}\in (V_1)^{k-1}$ be a tuple of vertices. 
		Then there exists $v\in V_1$ such that 
		$d(v,\overline{v})>2r^\prime+1$,
		$d(X,v)>2r^\prime +1$ and
		$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$
	\end{enumerate}
	Then Duplicator wins $\ehr_k\big(G^1;G^2\big)$.
\end{theorem}

@@

\begin{proof}[Proof of \cref{ThmDuplicator}]
	Define $r_0=0$ and $r_i=3r_{i-1}+1$ for $i>0$.
	Let us denote by $w_i$ and $z_i$ the vertices played
	in $G^1$ and $G^2$ respectively during the $i$-th
	round of $\ehr_k(G^1,G^2)$. 
	%Set 
	%$\overline{v}[i]:=v_1,\dots,v_i$ and
	%$\overline{u}[i]:=u_1,\dots,u_i$
	%We say that Duplicator can play following the strategy $S$
	%if they can play in a way that
	%at the end of the $s$-th round, $\overline{w}[s]$ and
	%$\overline{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
	%In particular this means that at the end of the $k$-th
	%round Duplicator will have won $\ehr_k(G^1,G^2)$.
	\par

	Let $X_1,\dots,X_a$ and 
	$Y_1,\dots,Y_b$ be partitions of 
	$X$ and $Y$ respectively
	as in the definition of $k$-agreeability.
	We will show a winning strategy for Duplicator
	in $d\ehr_{k}\big(G^1;\, G^2\big)$.	
	Let $r_k=1$ and for each $i\in [k-1]$ 
	let $r_i=3r_{i+1}+1$. In particular, 
	$r_1=r=(3^k-1)/2$.

@@

\todo[inline]{Quiz\'as reordenando esta demostraci\'on se puede acortar o se entiende mejor.}

>>>>

\subsection{Colored Hypergraphs and Copies.}

\begin{definition}
	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
	is a pair $(G, \chi)$ where $G$ is an hypergraph
	and $\chi: V(G)\rightarrow \Sigma$ is a map 
	called \textbf{$\Sigma$-coloring} of $G$. \par
	Given two $\Sigma$-hypergraphs $(G^1,\chi_1)$
	and $(G^2,\chi_2)$, and \textbf{isomorphism} between them is
	a bijection $f:V(G^1)\rightarrow V(G^2)$ satisfying
	that $f$ is an hypergraph isomorphism between $G^1$ and
	$G^2$ as well as
	$\chi_2(f(v))=\chi_1(v)$ for all $v\in V(G^1)$.\par	 
	Given a $\Sigma$-hypergraph $(G,\chi)$, an \textbf{automorphism}
	of $(G,\chi)$ is an isomorphism from it into itself. We will denote
	by $Aut(G,\chi)$ the group of such automorphisms. 
\end{definition}

@@

Let $G^1$ and $G^2$ be hypergraphs, and let
$V_1:=V(G^1), V_2:=V(G^2)$.
Let $\overline{v} \in V_1^*, 
\overline{u} \in V_2^*$ be tuples of the same length.
We say that $\overline{v}$ and $\overline{u}$ have
$k$-\textbf{similar} $r$-neighborhoods, written as
$(G^1,\overline{v})\simeq_{k,r}(G^2 \overline{u})$, if Duplicator wins
$d\ehr_k\big(N(\overline{v};r),
\overline{v};\, N(\overline{u};r),\overline{u}\big)$.
Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
we say that $X$ and $Y$ have $k$-similar
$r$-neighborhoods, written as
$X\simeq_{k,r} Y$, if we can order their elements to form
lists $\overline{v}$, resp. $\overline{u}$ such that 
$(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$. 
Given sets of vertices $X\in V_1$, $Y\in V_2$ and 
tuples of the same length $\overline{v}\in V_1^*$ and
$\overline{u}\in V_2^*$ we will say that $(X,\overline{v})$ 
and $(Y,\overline{u})$ have $k$-similar $r$-neighborhoods,
written as $\big(G_1, (X,\overline{v})  \big)
\simeq_{k,r} \big(G_2, (Y,\overline{u})  \big)$, if
the elements of $X$ and $Y$ can be ordered in lists
$\overline{w}$, $\overline{z}$ such that
$(G_1,\overline{w}^\smallfrown \overline{v})
\simeq_{k,r} (G_2,\overline{z}^\smallfrown \overline{u})$. \par
Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
$Y\subseteq V_2$ can
be partitioned into sets $X=X_1\cup \dots \cup X_a$
and $Y=Y_1\cup \dots \cup Y_b$ 
such that $N(X_i;r)$'s, and the
$N(Y_i;r)$'s, are connected and disjoint. 
We say that $X$ and
$Y$ have $k$-\textbf{agreeable} $r$-neighborhoods,
written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
among the $X_i$'s or the $Y_i$'s
it is satisfied that ``the number of $X_i$'s  
such that $(G^\delta, Z) \simeq_{k,r} (G^1,X_i)$ 
and the number of $Y_i$'s such that
$(G^\delta,Z)\simeq_{k,r} (G^2,Y_i)$
are both equal or are both greater 
or equal than $k$" .

@@

\begin{theorem}\label{ThmDuplicator}
	Set $r=(3^k-1)/2$.
	Let $G^1,G^2$ be hypergraphs and let $V_1:=V(G^1)$, $V_2:=
	V(G^2)$.
	Suppose there exist
	sets $X\subseteq V_1$, $Y\subseteq V_2$ with the 
	following properties:
	\begin{enumerate}
		\item[(1)] $(G^1,X)\cong_{k,r} (G^2,Y)$.
		\item[(2)]
		\begin{itemize}
			\item Let $r^\prime\leq r$. Let $v\in V_1$ be
			a vertex such that $d(X,v)> 2r^\prime + 1$. Let 
			$\overline{u}\in (V_2)^{k-1}$ be a tuple of vertices. 
			Then there exists $u\in V_2$ such that 
			$d(u,\overline{u})>2r^\prime+1$,
			$d(Y,u)>2r^\prime +1$ and
			$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$.	
			\item Let $r^\prime\leq r$. Let $u\in V_2$ be
			a vertex such that $d(Y,u)> 2r^\prime + 1$. Let 
			$\overline{v}\in (V_1)^{k-1}$ be a tuple of vertices. 
			Then there exists $v\in V_1$ such that 
			$d(v,\overline{v})>2r^\prime+1$,
			$d(X,v)>2r^\prime +1$ and
			$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$
		\end{itemize}
	\end{enumerate}
	Then Duplicator wins $\ehr_k\big(G^1;G^2\big)$.
\end{theorem}

@@

\begin{proof}[Proof of \cref{ThmDuplicator}]
	%Set 
	%$\overline{v}[i]:=v_1,\dots,v_i$ and
	%$\overline{u}[i]:=u_1,\dots,u_i$
	%We say that Duplicator can play following the strategy $S$
	%if they can play in a way that
	%at the end of the $s$-th round, $\overline{w}[s]$ and
	%$\overline{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
	%In particular this means that at the end of the $k$-th
	%round Duplicator will have won $\ehr_k(G^1,G^2)$.	
	Let $X_1,\dots,X_a$ and 
	$Y_1,\dots,Y_b$ be partitions of 
	$X$ and $Y$ respectively
	as in the definition of $k$-agreeability.
	Define $r_0=(3^k-1)/2$ and $r_i=(r_{i-1}-1)/3$ for each
	$1\leq i \leq k$. 
	Let us denote by $v^1_i$ and $v^2_i$ the vertices played
	in $G^1$ and $G^2$ respectively during the $i$-th
	round of $\ehr_k(G^1,G^2)$. 
	We will show a winning strategy for Duplicator
	in $d\ehr_{k}\big(G^1;\, G^2\big)$. For each $0\leq i \leq k$,
	Duplicator will	keep track of some marked sets 
	of vertices $T\subset V_1$, $S\subset V_2$. 
	For $\delta=1,2$ each marked set
	$T\subset V_\delta$ will have associated a tuple
	of vertices $\overline{v}(T)\in V_\delta^*$ consisting
	of the vertices played in $G_2$ so far, ordered according
	to the rounds they where played, that were 
	"appropriately close" to $T$ when chosen.
	The game will start with no sets of vertices marked and 
	at the end of the $i$-th
	round Duplicator will perform one of the two
	following operations:
	\begin{itemize}
	\item Mark two sets $S\subset V_1$ and $T\subset V_2$ and
	define $\overline{v}(S)=v^1_i$ and $\overline{v}(T)=v^2_i$.
	\item Given two sets $S\subset V_1$, $T\subset V_2$ that were 
	previously marked during the same round, append $v^1_i$
	and $v^2_i$ to $\overline{v}(S)$ and $\overline{v}(T)$ 
	respectively. 
	\end{itemize}
	In particular this means that at the 
	end of the $i$-th round the marked sets $S\subset V_1$
	, $T\subset V_2$ and their respective lists $\overline{v}(S)$,
	$\overline{v}(T)$ satisfy
	\begin{itemize}
		\item[(i)] For $\delta=1,2$, each vertex played
		so far $v^\delta_j\in V_\delta$ belongs to 
		$\overline{v}(S)$ for a	 unique marked set 
		$S\subset V_\delta$.
		\item[(ii)] Let $S\subset V_1$ and $T\subset V_2$ be sets
		marked during the same round. Then any previously played
		vertex $v^1_j$ occupies a position in $\overline{v}(S)$
		if and only if $v^2_j$ occupies the same position 
		in $\overline{v}(T)$.
	\end{itemize}
	The following conditions will also be satisfied at the 
	end of the $i$-th round
	\begin{itemize}
		\item[(iii)] 
			\begin{itemize}
			\item  Let $S\subset V_1$ be a marked set. Then 
			for any different marked $S^\prime \subset V_1$ 
			of any different $S^\prime$ among $X_1,\dots,X_a$
			it holds $d(S,S^\prime)>2r_i + 1$. 
			\item Let $T\subset V_2$ be a marked set. Then
			for any different marked $T^\prime \subset V_2$
			or any different $T^\prime$ among
			$Y_1,\dots, Y_b$  it holds $d(T,T^\prime)>2r_i +1$.
			\end{itemize}
		\item[(iv)] Let $S\subset V_1, T\subset V_2$ be sets
		marked during the same round. Then
		\[
		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
		\big(G^2, (T,\overline{v}(T))\big).	\]

	\end{itemize}
	In particular, if conditions (i) to (iv) are satisfied this means
	that if $\overline{v}^1=(v^1_1,\dots,v^1_i)$ and
	$\overline{v}^2=(v^2_1,\dots, v^2_i)$ are the vertices played so far
	then Duplicator wins
	\[
	d\ehr_{k-i}\big(\,
	N(\overline{v}^1;\, r_i), \overline{v}^1; \quad
	N(\overline{v}^2;\, r_i),\overline{v}^2 \,
	\big),	
	\]
	And at the end of the $k$-th round Duplicator will have won
	$\ehr(G^1;\, G^2)$. \par
	The game $d\ehr_k(G_1; \, G_2)$ proceeds as follows. Suppose 
	that during the $i$-th round Spoiler chooses $v^1_i\in V_1$ 
	(the case where they play in $V_2$ is symmetric). There are 
	three possible cases:
	\begin{itemize}
		\item For some unique previously marked set $S\subset V_1$ 
		it holds that $d(S\cup \overline{v},\quad v^1_i)\leq 2r_i +1$. 
		In this case let $T\subset V_2$ be the set in $G_2$ marked in the 
		same round as $T$. By hypothesis 
		\[ \big(G^1,(S,\overline{v}(S))\big)
		\simeq_{k-i+1,3r_i+1}
		\big(G^2,(T,\overline{v}(T))\big). 		
		\]
		Then, by definition,
		for some orderings $\overline{w}$, $\overline{z}$
		of the vertices in $S$ and $T$ respectively it holds that
		Duplicator wins
		\[
		d\ehr_{k-i+1}\big(\,
		N(\overline{w}^\smallfrown \overline{v}(S); \, 3r_i	+ 1)
		, \overline{w}^\smallfrown \overline{v}(S); \quad
		N(\overline{z}^\smallfrown \overline{v}(T); \, 3r_i	+ 1)
		, \overline{z}^\smallfrown \overline{v}(T)\,	
		\big).		
		\]
		Thus Duplicator can choose $v^2_i\in V_2$ according to the 
		winning strategy in that game. After this Duplicator sets 
		$\overline{v}(S):= \overline{v}(S)^\smallfrown v^1_i$, and
		$\overline{v}(T):= \overline{v}(T)^\smallfrown v^2_i$. Notice
		that because of \cref{lemm:Duplicator} now
		\[
		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
		\big(G^2, (T,\overline{v}(T))\big).
		\]
		\item For all marked sets $S\subset V_1$ it holds
		$d(S\cup \overline{v}(S), \quad v^1_i)>2r_i +1$, but there is
		a unique $S$ among $X_1,\dots, X_a$ such that
		$d(S,v^1_i)\leq 2r_i+1$. In this case from condition (1)
		of the statement follows that there is some non-marked
		set $T$ among $Y_1,\dots, Y_b$ such that
		\[
		(G^1,S)\simeq_{k-i+1,3r_i+1} (G^2,T).\] 
		Thus, by definition, for some orderings $\overline{w}$, 
		$\overline{z}$ of the vertices in $S$ and $T$ respectively
		it holds that Duplicator wins
		\[
		d\ehr_{k-i+1}\big( \,
		N(\overline{w};3r_i+1), \overline{w};
		\quad
		N(\overline{z};3r_i+1), \overline{z}
		\, \big).		
		\]
		Then Duplicator can choose $v^2_i\in V_2$ according 
		to a winning strategy for this game. After this Duplicator
		marks both $S$ and $T$ and sets 
		$\overline{v}(S):=v^1_i$, and 
		$\overline{v}(T):=v^2_i$. Notice
		that because of \cref{lemm:Duplicator} now
		\[
		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
		\big(G^2, (T,\overline{v}(T))\big).
		\]
		\item For all marked sets $S\subset V_1$ it holds
		$d(S\cup \overline{v}(S), \quad v^1_i)>2r_i +1$, and
		for all sets $S$ among $X_1,\dots, X_a$ it also holds
		$d(S,v^1_i)> 2r_i+1$. In this case
		from condition (2) of the statement follows that
		Duplicator can choose
		$v^2_i\in V_2$ such that
		(A)
		$d(T\cup \overline{v}(T),\quad v^2_i)>2r_i+1$ for all
		marked sets $T\subset V_2$, (B)
		$d(T, v^2_i)> 2r_i+1$ for all sets $T$ among
		$Y_1,\dots, Y_b$, and (C) 
		$(G^1,v^1_i)\simeq_{k-i,r_i} (G^2, v^2_i)$.
		After this Duplicator marks both $S=\{
		v^1_i\}$ and $T=\{v^2_i\}$ and sets
		$\overline{v}(S):=v^1_i$, and
		$\overline{v}(T):=v^2_i$. 		
	\end{itemize}	 
	The fact that conditions
	(i) to (iv) still hold at the end of the round
	follows from comparing $r_{i-1}$ and $r_{i}$ as well 
	as applying \cref{obs1} and \cref{obs2}.

@@
